Cluster Difference Imaging Photometric Survey. III. An Open Cluster With a 300\,pc Halo

### 2021-03-05 cluster_paper/ms.tex
verified Gaia target list vs CDIPS results

% n rotation period logs: 2238 % ~/proj/cdips/results/allvariability_reports/NGC_2516/logs
% ... which came from ~/Dropbox/proj/cdips/data/cluster_data/cdips_catalog_split/OC_MG_FINAL_v0.4_publishable_CUT_NGC_2516.csv
% n all variability reports: 2201 % ~/proj/cdips/results/allvariability_reports/NGC_2516/reports
\newcommand{\ncdips}{2,238\ } % e.g., from OC_MG_FINAL_v0.4_publishable_CUT_NGC_2516.csv. checked with plot_target_vs_actual_list_sanity_checks.py

@@

We began our rotation analysis by considering all \nkinematic\
candidate cluster members.  For each source, we first retrieved all
available CDIPS light curves, on a per-sector basis.

%FIXME: except actually, will need to redo with the new source list
%too .......

This yielded \ncdips light curves, all brighter
than $Rp=16$\,mag.  The $Rp=16$\,mag cutoff imposed during the CDIPS
processing corresponds roughly to $(Bp-Rp)_0$ of 2.2, or a spectral
type of $\approx$M2V, at the distance of NGC\,2516.

We cleaned and stitched the light curves as follows.
First, we detrended the systematics in each sector individually, and
stitched together the resulting light curves before searching for the
periodicity.  Some details regarding our detrending approach are
discussed in Appendix~\ref{app:detrending}.  After applying a
detrending step aimed at removing systematic trends, we proceeding
with a few small cleaning steps aimed at improving the purity of the
rotation period measurements: we masked 0.7 days at the beginning and
end of each spacecraft orbit, and ran a sliding standard-deviation
rejection window over the light curve, which removed any outlying
points within $\pm3\times$MAD of the median in each window.

We then measured the rotation period of the resulting light curve.  We
used the the aperture radius that, based on theoretical expectations,
was expected to give the optimal balance between light from the target
and background-light (CITE Sullivan15).  This typically resulted in an
aperture radius of either 1 or 1.5 pixels.  To measure the periods, we
used the periodogram implementations in \texttt{astrobase}, in
particular the Stellingwerf PDM periodogram (CITE), along with the
more traditional Lomb-Scargle (CITE).  We recorded the top five
periodogram peaks from each method, and their corresponding powers.
Finally, as a check on crowding, we also recorded the number of stars
within the aperture of equal brightness to the target stars, and of
brightness with 1.25 and 2.5 TESS magnitudes of the target star.

@@

\subsection{Absolute age of NGC 2516}
Cummings & Kalirai (2018) favor 150 Myr based on MSTO.
Godoy-Rivera+2021 favor 150 Myr... based on ...? what?
"""
Similar to Cummings et al. (2016), Cummings & Kalirai (2018),
and Cummings et al. (2018) (see also Fritzewski et al. 2020 and Healy
&
McCullough 2020)
"""

>>>>

% from drivers.cluster_rotation.get_auto_rotation_periods.py
% checked with plot_target_vs_actual_list_sanity_checks.py
\newcommand{\ncdips}{2{,}205\ }
\newcommand{\nkinematicrpltsixteen}{2{,}270\ }
\newcommand{\nkinematicCGandKC}{2{,}236\ }

@@

We began our rotation analysis by considering all \nkinematic\
candidate members of \cn.  For each source, we first retrieved all
available CDIPS light curves, on a per-sector basis.  This yielded
\ncdips stars with at least one sector from a CDIPS light curve, all
brighter than $Rp=16$\,mag.  \nkinematicrpltsixteen\ of the
stars from the source list have $Rp<16$.  The difference is comprised
of 34 stars unique to \citet{meingast_2021} which were not
available at the time of the CDIPS reductions and stars falling on
the TESS chip gaps.  The $Rp=16$\,mag cutoff imposed during the CDIPS
processing corresponds roughly to $(Bp-Rp)_0$ of 2.2, or a spectral
type of $\approx$M2V, at the distance of NGC\,2516.

We removed systematic trends shared between
all light curves on each CCD in each sector individually, and
stitched together the resulting light curves before searching for the
periodicity.  Details regarding our detrending approach are
discussed in Appendix~\ref{app:detrending}.  After applying the
initial
detrending step aimed at removing systematic trends, we proceeding
with a few small cleaning steps aimed at improving the purity of the
rotation period measurements: we masked 0.7 days at the beginning and
end of each spacecraft orbit, and ran a sliding standard-deviation
rejection window over the light curve, which removed any outlying
points within $\pm3\times$MAD of the median in each window.

We then measured the rotation period of the resulting light curve.  We
used the CDIPS aperture radius that, based on theoretical expectations,
was expected to give the optimal balance between light from the target
and background-light \citep{Sullivan_2015}.  This typically resulted in an
aperture radius of either 1 or 1.5 pixels.  To measure the periods, we
used the periodogram implementations in \texttt{astrobase}, in
particular the Stellingwerf PDM periodogram (CITE), along with the
more traditional Lomb-Scargle (CITE).  We recorded the top five
periodogram peaks from each method, and their corresponding powers.
Finally, as a check on crowding, we also recorded the number of stars
within the aperture of equal brightness to the target stars, and of
brightness with 1.25 and 2.5 TESS magnitudes of the target star.

@@

\subsection{Absolute age of NGC 2516}
Cummings \& Kalirai (2018) favor 150 Myr based on MSTO.
Godoy-Rivera+2021 favor 150 Myr... based on ...? what?
"""
Similar to Cummings et al. (2016), Cummings \& Kalirai (2018),
and Cummings et al. (2018) (see also Fritzewski et al. 2020 and Healy
\&
McCullough 2020)
"""
